
\section{Work and Research Experience}

\outerlist{

\entrybig
  {\textbf{Two Sigma Investments}}{New York, NY}
    {Software Engineering Intern (Platform Engineering - SDLC)}{May 2022 - Aug 2022}
    \innerlist{
      \entry{ Completely overhauled the user experience for generating new services through the CLI. }
      \entry{ Created a full GUI experience within the terminal with dynamic input validation and navigation buttons. }
      \entry{ Used Datadog tracing and logging to provide on-call supporters with maximum visibility and alerts for anomalies. }
      \entry{ Iterated through beta testing feedback and fully deployed project to the entire company. }
      \entry{ Completed the stretch goal, allowing users to detect and automatically perform service migrations. }
    }
\entrybig
	{\textbf{Amazon, Inc.}}{Santa Clara, CA}
    {AWS Software Development Intern (Machine Learning Device Inference)}{May 2021 - July 2021}
\innerlist{
    \entry{ Exceeded expectations by completing two commercially impactful projects in eleven weeks. }
    \entry{\textbf{ Project 1: Containerization and Nightly Testing (7 Weeks)} 
        \innerlist{
            \entry{ Used Docker and AWS services (EC2, S3, ECR) to containerize the AWS machine learning inference binary on multiple OS to be self contained with dependencies. }
            \entry{ Significantly improved customer experience by removing dependency issues and allowing faster deployment. }
            \entry{ Deployed Python testing script to run integration and unit tests on devices using containers every night. }
            \entry{ Successfully released to customers and available to download and deploy. }
        }
    }
    \entry{\textbf{ Project 2: Python Bindings (4 Weeks) } 
        \innerlist{
            \entry { Generated bindings for existing C machine learning APIs using pybind11. }
            \entry { Bindings allowed customers to use Python interface instead of C with an easy to install and use module. }
            \entry { Highly requested by customers and easy to get up and running. }
        }
    }
}

\entrybig
	{\textbf{UMich Biomedical and Clinical Informatics Lab}}{Ann Arbor, MI}
	{Undergraduate Researcher}{Sep. 2020 - May 2021}
\innerlist{
    \entry{ Participated in a leading bioinformatics research lab focusing on using computing for medical purposes. }
    \entry{ Used MATLAB to improve a lung segmentation algorithm, automating the process of outlining lung boundaries.}
	\entry{ Extracted features from chest x-rays and trained a model that is 85\% effective at diagnosing patients with ARDS, a highly deadly respiratory syndrome. Used the scipy library in Python. }
}

\entrybig
	{\textbf{Vivalink, Inc.}}{Campbell, CA}
	{Software Engineering Intern}{Dec. 2020 - Feb. 2021}
\innerlist{
	\entry{Converted novel blood pressure algorithm from Python to C++ to allow the efficient deployment of the algorithm onto a mobile platform. }
}

}

